Live probes for free

### 2023-07-18 paper/example-programming.tex
Add performance plot

\begin{itemize}
  \item What is the average performance during a live programming session?
  \item What is the compilation time as a function of programme size?
  \item How long does it take to load the code into the debugger, depending on the size of the programme?
  \item How long does it need to run the program, depending on the number of steps to make the stack recording ?
\end{itemize}

@@

>>>>

\begin{itemize}
  \item What is the average performance during a live programming session?
  \item What is the compilation time as a function of programme size ?
  \item How long does it take to load the code into the debugger, depending on the size of the programme?
  \item How long does it need to run the program, depending on the number of steps to make the stack recording ?
\end{itemize}

@@

\subsubsection{What is the compilation time as a function of programme size ?}
\subsubsection{How long does it take to load the code into the debugger, depending on the size of the programme?}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{img/load_code.png}
  \caption{Load code time in seconds depending on the size of the program.}
  \label{fig:load-code}
\end{figure}

\subsubsection{How long does it need to run the program, depending on the number of steps to make the stack recording ?}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{img/execute.png}
  \caption{Execution time in seconds depending on the number of steps.}
  \label{fig:execute}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.8\linewidth]{img/execute_ps.png}
  \caption{Execution time in seconds per step.}
  \label{fig:execute_tps}
\end{figure}
